---
title: "IP - Anomaly Detection"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Data Analysis Objectives
Perform anomaly detection analysis on sales data and report any inconsistencies.

### Understanding context
Carrefour Kenya seeks to undertake a project that will inform the marketing department on the most relevant marketing strategies that will result in the highest no. of sales (total price including tax). Anomaly detection analysis on sales data would be helpful in identifying if there is occurrence of any fraudulent transactions and when they occured to perform further investigation. 

### Experimental Design

- Business Understanding
- Loading Data
- EDA
- Implementation of the solution
- Findings

```{r}
# Load packages
library(tidyverse)
library(anomalize)
library(tibbletime)
library(lubridate)
```
```{r}
# Load data
sales_data <- read.csv('Supermarket_Sales_Forecasting - Sales.csv', stringsAsFactors = FALSE)
head(sales_data)
```
```{r}
summary(sales_data$Sales)
```
```{r}
# Convertieng date column into date object
sales_data$Date <- as_date(mdy(sales_data$Date))
```
```{r}
# Get the range of dates in the data
paste(c('Start:'), min(sales_data$Date))
paste(c('End:'), max(sales_data$Date))
```
Sales data ranges over a period of 3 months.
```{r}
# Visualize sales data
ggplot(data = sales_data, aes(x=Date, y = Sales))+
  geom_line(color = "#00AFBB", size = 1)+
  stat_smooth(color = "#FC4E07", fill = "#FC4E07",
  method = "loess")
```
```{r}
# Get total sales and average sales made per day
summary_sales <- sales_data %>% group_by(Date) %>% summarise_all(list(mean = mean, sum = sum))
head(summary_sales,  3)
```


```{r}
# Anomaly detection using total sales per day
summary_sales %>% 
  as_tbl_time(Date) %>% 
  time_decompose(sum) %>% 
  anomalize(remainder) %>% 
  time_recompose()%>%
  plot_anomalies(time_recomposed = TRUE, ncol = 3, alpha_dots = 0.5)
```
NO anomalies present in the data

```{r}
# Anomaly detection using average sales per day
summary_sales %>% 
  as_tbl_time(Date) %>% 
  time_decompose(mean) %>% 
  anomalize(remainder) %>% 
  time_recompose()%>%
  plot_anomalies(time_recomposed = TRUE, ncol = 3, alpha_dots = 0.5)
```
NO anomalies detected in the data

### Summary of Findings.
Analysis of the data indicates no fraudulent activity in the data