---
title: "IP - Association Rules"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Objective
To perform Associative analysis on sales data to identify customer purchase behavior.

### Context
Carrefour Kenya, a mega retailer, seeks to identify the most relevant marketing strategies that will result in higher volume of sales.

### Experimental Design

- Business Understanding
- Loading of Data
- EDA
- Implementation of the solution
- Findings

```{r}
# Load the libraries
library(arules)
library(arulesViz)
```
```{r}
# Load the data
transactions <- read.transactions("Supermarket_Sales_Dataset II.csv", sep="," , header = FALSE)
transactions
```
```{r}
# Checking the transactions class
class(transactions)
```

```{r}
# Preview  first 5 transactions
inspect(transactions[1:5])
```
```{r}
# Number of unique items bought
length(itemLabels(transactions))
```
This basket contains 119 unique items

```{r}
# Summary of the transactions
summary(transactions)
```
Mineral Water, Eggs, Spaghetti, French Fries and Chocolate are the top 5 most purchased items

```{r}
# Plot the top 10 most frequently purchased items
par(mfrow = c(1, 2))

# plot the frequency of items
itemFrequencyPlot(transactions, topN = 10,col="darkgreen")
itemFrequencyPlot(transactions, support = 0.1,col="darkred")
```
Mineral water, eggs and spaghetti are the top 3 frequently purchased items. 

```{r}
# Plotting items with minimum support of 0.1
itemFrequencyPlot(transactions, support = 0.1, col = "brown3")
```


```{r}
# Support per item
support <- sort(itemFrequency(transactions) * 100)

# Percentage of items with a support less than 0.1%
length(support[support < 0.1])/ 119 * 100

# Percentage of items with a support less than 0.2%
length(support[support < 0.2])/ 119 * 100
```

```{r}
# Building Models based on association rules
# Using minimum support of 0.001 and confidence of 0.8
rules_set1 <- apriori(transactions, parameter = list(supp = 0.001, conf = 0.8, maxlen=10))

# Using minimum support of 0.002 and confidence of 0.6
rules_set2 <- apriori(transactions, parameter = list(supp = 0.002, conf = 0.6, maxlen=10))
```

```{r}
# Viewing the Summary
summary(rules_set1)
```

A minimum support and confidence of 0.001 and .8 respectively generate 74 rules

```{r}
summary(rules_set2)
```
A minimum support and confidence of 0.002 and .6 respectively generate 43 rules

```{r}
# Sort rules based on confidence
inspect(sort(rules_set1, by="confidence", decreasing = T)[1:10])
```
```{r}
# Visualize top 10 rules
top10rules <- head(rules_set1, n = 10, by='confidence')
plot(top10rules, method = "graph",  engine = "htmlwidget")
```
Mushroom cream sauce and pasta are most frequently bought before escalope.


```{r}
inspect(sort(rules_set2, by='confidence', decreasing = T)[1:10])
```

```{r}
top10rules <- head(rules_set2, n=10, by='confidence')
plot(top10rules, method = 'graph', engine = 'htmlwidget')
```


```{r}
# Creating Shorter Association Rules
shorter_ruleset <- apriori(transactions, parameter = list(supp = 0.001, conf = 0.8, maxlen=4))
```
```{r}
inspect(sort(shorter_ruleset, by='confidence', decreasing = T)[1:20])
```

```{r}
top10rules <- head(shorter_ruleset, n=10, by='confidence')
plot(top10rules, method = 'graph', engine = 'htmlwidget')
```
```{r}
# Get association rules associated to shrimp
shrimp_ruleset <- apriori(transactions, parameter = list(supp=0.001, conf=0.8), appearance = list(default="lhs", rhs="shrimp"))
```
```{r}
inspect(shrimp_ruleset)
```
Customers purchase pasta before purchasing shrimp

```{r}
# Get association rules associated to spaghetti
spaghetti_ruleset <- apriori(transactions, parameter = list(supp=0.001, conf=0.8), appearance = list(default="lhs", rhs="spaghetti"))
plot(spaghetti_ruleset, method = 'graph', engine = 'htmlwidget')
```
Items most bought before spaghetti are shrimp, salmon and ground beef.

### Summary of findings
1. Mushroom cream sauce and pasta are most often bought together with escalope. Stocking pasta and mushroom cream sauce in the same section or next to each other could increase sales.
2. Shrimp, salmon and ground beef are most often bought before spaghetti, locating the meats section next to the pasta/spaghetti section could boost sales.
3. Package deals of mushroom sauce and spaghetti together.