---
title: "Dimensionality Reduction - IP"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(FactoMineR)
library(tidyverse)
library(factoextra)
```

```{r}
# Load data
sales = read.csv('Supermarket_Dataset_1_Sales_Data.csv')
head(sales)
```
```{r}
# Investigate gross margin percentage
unique(sales$gross.margin.percentage)
# Set gross margin percentage column
sales$gross.margin.percentage <- NULL
```

```{r}
str(sales)
```
```{r}
# Check for equality of gross.income and tax
all(sales$Tax == sales$gross.income)
```
```{r}
# Set gross income to null
sales$gross.income <- NULL
```
```{r}
summary(sales[, -c(1,9,10)])
```

```{r}
# Rearrange data columns
sales.new <- sales[, c(2,3,4,5,11,6,7,8,12,14,13)]
row.names(sales.new) <- sales$Invoice.ID
# Perform PCA on qualitative variables
pca <- prcomp(sales.new[, c(6:10)], scale = TRUE)
```

```{r}
summary(pca)
```

```{r}
# Visualize variances of each principal component
fviz_eig(pca)
```

The first principal component explains over 65% variation in the dataset. 
```{r}
fviz_pca_var(pca,
             col.var ="contrib", # Color by the quality of representation
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             repel = TRUE     # Avoid text overlapping
             )
```

Total variable is a combination of tax and cogs variables. A large number of variables in the data are categorical, factor analysis on mixed data for these variables could be helpful.

```{r}
# Perform factor analysis
famd <- FAMD(sales.new,ncp = 7, graph = F)
```

```{r}
# eigen values for each dimension
get_eigenvalue(famd)
```

```{r}
fviz_eig(famd)
```
```{r}
# Plot of variables
fviz_famd_var(famd, repel = TRUE)
# Contribution to the first dimension
fviz_contrib(famd, "var", axes = 1)
# Contribution to the second dimension
fviz_contrib(famd, "var", axes = 2)
```

From the plots above, it can be seen that:

- variables that contribute the most to the first dimension are: tax, cogs and total

- variables that contribute the most to the second dimension are: gender, product line, payment