---
title: "IP - Feature Selection"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Analysis Objectives
Customer ratings on shopping experience is integral to the the sales that a supermarket makes. Predicting the cutomer rating would be helpful to the Carrefour marketing team in determing how consumers review their shopping experience and their sentiment on different product categories.

```{r}
library(caret)
library(corrplot)
# Load data
sales.data <- read.csv('Supermarket_Dataset_1_Sales_Data.csv')
head(sales.data)
```
```{r}
# Set gross.margin percentage and gross income to null
sales.data$gross.margin.percentage <- NULL
sales.data$gross.income <- NULL
```

```{r}
summary(sales.data[, c(2:8, 11:12)])
```

```{r}
row.names(sales.data)<- sales.data$Invoice.ID
sales.data$Invoice.ID <- NULL
sales.data$Date <- NULL
sales.data$Time <- NULL
# Encode categorical variables
sales.data$Customer.type <- ifelse(sales.data$Customer.type == 'Member', 1,0)
sales.data$Gender <- ifelse(sales.data$Gender == 'Male', 1,0)
dmy <- dummyVars(" ~ .", data = sales.data)
sales_transformed <- data.frame(predict(dmy, newdata = sales.data))
glimpse(sales_transformed)
```

```{r}
# Calculating the correlation matrix
# ---
#
correlationMatrix <- cor(sales_transformed)
# Find attributes that are highly correlated
# ---
#
highlyCorrelated <- findCorrelation(correlationMatrix, cutoff= 0.75)
# Highly correlated attributes
# ---
# 
highlyCorrelated
names(sales_transformed[,highlyCorrelated])
```
Tax and cogs columns are highly correlated. cogs is the price before addition of tax while total is the addition of cogs and tax

```{r}
corrplot(correlationMatrix, type='upper', tl.cex=0.6, tl.col = 'black')
```
```{r}
# Correlation plot after removal of cogs
correlationMatrix2 <- cor(sales_transformed[,c(1:17, 19:20)])
corrplot(correlationMatrix2, type='upper', tl.col = 'black', tl.cex = 0.6)
```